Risk Perceptions for Wearable Devices

### 2015-03-03 tables-more/wearables-survey-paper-master/results.tex
started to look at results

\section{Results}
In this section, we present our survey results. We first discuss participants' responses to the various data-sharing scenarios, and how data type, data recipient, and device contributed to how threatening a situation was perceived. Next, we discuss participants' risk/benefit assessment of various new technologies relative to well-established technologies. We conclude the section with participants' self-reported concerns about the biggest risks in owning wearable devices.

\subsection{Concern Factors}
In this section, we discuss factors impacting participants' concern levels for each scenario: the data recipient, the data type, and whether or not the scenario occurred on a wearable or a smartphone. We analyze each factor individually, as well as present a statistical model of participants' concerns as a function of all of factors, including demographic traits.

\subsubsection{Data Type}
Based on our data, we observed that the largest effect stemmed from the data type being shared in a scenario. We present various statistical models in section \ref{sec:regression} to support this conclusion. Due to space limitations, we are unable to show results of the statistical analyses respect to the significance of the VUR rankings of the 88 data types. The 10 most and 10 least concerning data types can be seen in Table \ref{top10}.

@@

Without a doubt, the most common self-reported concern of wearables for the average user is the \textit{possible loss of privacy}. This top concern surpassed all other concerns by about an order of magnitude or more (see Table \ref{openresponses}). Other significant secondary concerns included being unaware of what the device is collecting, doing, or which information it is using (Being Unaware), long-term health effects caused from wearing the device such as cancer from emf waves (Health), safety hazards from wearing the device such distractions causing car accidents (Safety), resulting changes in social behaviors, such as dependencies on devices or spending less time with loved ones (Social Impact), the high financial cost of buying, replacing, or caring for the device (Financial), and information compromise (Security).

>>>>

\section{Results}
We present our survey results and provide analyses of the data. We first discuss participants' responses to the various data-sharing scenarios, and how data type, data recipient, and device contributed to how threatening a situation was perceived. Next, we discuss participants' risk/benefit assessment of various new technologies relative to well-established technologies. We conclude the section with participants' self-reported concerns about the biggest risks in owning wearable devices.

\subsection{Concern Factors}
Many factors impact participants' concern levels for each scenario: the data recipient, the data type, and whether or not the scenario occurred on a wearable or a smartphone. We analyze each factor individually, as well as present a statistical model of participants' concerns as a function of all of factors, including demographic traits.

\subsubsection{Data Type}
Based on our data, we observed that the largest effect stemmed from the data type being shared in a scenario. We present various statistical models in section \ref{sec:regression} to support this conclusion. The 10 most and 10 least concerning data types can be seen in Table \ref{top10}.

@@

Without a doubt, the most common self-reported concern of wearables for the average user is the \textit{possible loss of privacy} (see Table \ref{openresponses}). Other significant secondary concerns included being unaware of what the device is collecting, doing, or which information it is using (Being Unaware), long-term health effects caused from wearing the device such as cancer from emf waves (Health), safety hazards from wearing the device such distractions causing car accidents (Safety), resulting changes in social behaviors, such as dependencies on devices or spending less time with loved ones (Social Impact), the high financial cost of buying, replacing, or caring for the device (Financial), and information compromise (Security).

### 2015-03-03 tex-inputs/results-recipient.tex
started to look at results

{\color {red} we're not saying that there is no distinction, just that there is more distinction between people and the app server."users make little distinction between sharing data with friends, co-workers, or the general public”: at first sight, this result is in conflict with privacy studies specifically in the social arena (e.g., Facebook). The authors may want to comment on this fact if they have any explanation.}

{\color {red} add a discussion here about the variance between the recipients. Mention specific numbers. Was there a change in distribution just because we changed the recipient type?}

>>>>

{\color {red} We do not claim that there is no distinction between the friends, public, and work contact recipients, because people have been shown to behave differently, especially in the social arena (cite studies here). People are more comfortable sharing certain data types with certain recipients (refer to the table of all questions with ranks by each recipient here). There are other data types which are universally concerning, and universally unconcerning, and the magnitude of the sentiment varies by recipient. As you can see in Table (J still needs to do this table), the VUR rate for each recipient is negatively correlated with the standard deviation of the answers.  Additionally, we see that there is greater distinction between sharing people and the app server--people are comfortable sharing data they would feel uncomfortable sharing with at human recipient, and the magnitude of concerns is might more significant compared to the other recipients.}

### 2015-03-03 tex-inputs/results-type.tex
sprinkled things to talk about inline
started to look at results

Regardless of the data recipient or the device, participants were most concerned about photos and videos, especially if they contained embarrassing content, nudity, or financial information. As seen in Table \ref{top10}, photos and videos accounted for 5 of the top 10 concerns. Information that could be used to impersonate someone (e.g., usernames/passwords for websites) or invade privacy (photos of someone at home) were also among the most concerning data types.

Also regardless of the data recipient, the least concerning data types mostly consisted of information that could be observed through observations of public behavior, such as demographic information (e.g., age, gender, language spoken). It is possible that people rated these as unconcerning because they think many entities already track this data (e.g., shows watched, music listened to, exercise patterns).

>>>>

Regardless of the data recipient or the device, participants were most concerned about photos and videos, especially if they contained embarrassing content, nudity, or financial information. As seen in Table \ref{top10}, photos and videos accounted for 5 of the top 10 concerns, {\color {red} and are unanimously considered to be concerning}. Information that could be used to impersonate someone (e.g., usernames/passwords for websites) or invade privacy (photos of someone at home) were also among the most concerning data types.

Also regardless of the other factors, the least concerning data types mostly consisted of information that could be observed through observations of public behavior, such as demographic information (e.g., age, gender, language spoken). {\color {red} As seen in Table \ref{top10}, participants had distributed opinions on how risky this information was to be shared. A possibility is that people rated these as unconcerning because of unfamiliarity in what applications would use this data for, or because there does not seem to be any immediate financial, social, or physical consequences from having this information shared.}

{\color {red} talk about the variance of the data types here, referring to the table in the appendix. Which were the highest in variance? Which were the unanimous? Which one had a spread? Were there any that were specifically polarized? J has yet to give me the table for this so I can talk about it. But the most unanimous ones seemed to be the highest-concerning ones, whereas the least concerning ones were more distributed. There are not any which are unanimously considered medium risk or to be not risky.}
